Left-linear rules in adhesive categories

### 2024-02-11 icalp/fusione.tex
minima

\begin{remark}
  \label{rem:salva}
  \emph{Adhesivity} and \emph{quasiadhesivity} 
  \cite{lack2005adhesive,garner2012axioms} coincide with strict
  $\mon(\X) $-adhesivity and strict $\reg(\X)$-adhesivity,
  respectively, for $\reg(\X)$ the class of regular monos.
\end{remark}

@@

\begin{restatable}[Globality of indepedence]{lemma}{lemIndepGlobalLeft}
  \label{lem:indep-global-left}
  Let $\X$ be an $\mathcal{M}$-adhesive category and
  $(\X,\R)$ a left-linear DPO rewriting system.
  Consider a derivation
  $\der{D}=\{\dder{D}_i\}_{i=0}^2$ and suppose that $(i_0,i_1)$ is a
  good independence pair between $\dder{D}_0$ and $\dder{D}_1$,
  $(a_0,a_1)$ one between $\dder{D}_1$ and $\dder{D}_2$ and
  $(e_0, e_1)$ one between $\dder{D}_0$ and
  $S_{a_0,a_1}(\dder{D}_2)$. Then the following properties hold true.
  \begin{enumerate}
  \item
    \label{lem:indep-global-left:1}
    $S_{e_0,e_1}(\dder{D}_0)$ and $S_{a_0,a_1}(\dder{D}_1)$ are
    sequentially independent.

@@

While in the case of linear rewriting systems inversion can be
performed in any order, this is no longer true for left-linear
rewriting systems.\todo{P: copunter example} Still, we can identify a
canonical form for switching derivations.

>>>>

\begin{remark}
  \label{rem:salva}
  \emph{Adhesivity} and \emph{quasiadhesivity} 
  \cite{lack2005adhesive,garner2012axioms} coincide with strict
  $\mon(\X) $-adhesivity and strict $\reg(\X)$-adhesivity,
  respectively.
  % for $\reg(\X)$ the class of regular monos.
\end{remark}

@@

\begin{restatable}[Globality of independence]{lemma}{lemIndepGlobalLeft}
  \label{lem:indep-global-left}
  Let $\X$ be an $\mathcal{M}$-adhesive category and
  $(\X,\R)$ a left-linear DPO rewriting system.
  Consider a derivation
  $\der{D}=\{\dder{D}_i\}_{i=0}^2$ and suppose that $(i_0,i_1)$ is a
  good independence pair between $\dder{D}_0$ and $\dder{D}_1$,
  $(a_0,a_1)$ one between $\dder{D}_1$ and $\dder{D}_2$ and
  $(e_0, e_1)$ one between $\dder{D}_0$ and
  $S_{a_0,a_1}(\dder{D}_2)$. Then the following properties hold true.
  \begin{enumerate}
  \item
    \label{lem:indep-global-left:1}
    $S_{e_0,e_1}(\dder{D}_0)$ and $S_{a_0,a_1}(\dder{D}_1)$ are
    sequentially independent.

@@

While in the case of linear rewriting systems inversion can be
performed in any order, this is no longer true for left-linear
rewriting systems.\todo{P: counter example} Still, we can identify a
canonical form for switching derivations.
